---
title: "AW_HealthDataPrep_14Feb"
author: "me"
date: "14/02/2019"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
  title: "AW_HealthDataPrep"
author: "Bo Simango"
date: "February 27, 2019"
output: 
  html_document:
  keep_md: yes
pdf_document: default
---
  
```{r}
# Created by Bo Simango
# M.Sc. candidate 
# Supervisor: Dr. Daniel Fuller
# Memorial University of Newfoundland
# Date: February 5, 2019
# Function: This code appends the Health Data Collector app data by participant ID (107-111) and plots the HR, Steps and Calories vs. Time using two R packages ggplot2 and facet_wrap
# Data source: Health Data Collector App - AW data 
# Output: Appended CSVs, ggplot facet wrap and mice imputation 
# First install all libraries used throughout this exercise 
```
#========================Libraries=========================
```{r}
library(knitr)
library(haven)
library(ggplot2)
library(plyr)
library(dplyr)
library(readr)
install.packages("stargazer")
library(stargazer)
library(missForest)
```
# ========================Working Directory=========================

```{r}
# Set working directory
setwd("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData")
```
# ====================Read Health Data Collector App data================== 

```{r}
# Read Health Data Collector App data 
a_107 <- read.csv("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/107/applewatch_data107.csv")
a_108 <- read.csv("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/108/applewatch_data108.csv")
a_109 <- read.csv("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/109/applewatch_data109.csv")
a_110 <- read.csv("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/110/applewatch_data110.csv")
a_111 <- read.csv("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/111/applewatch_data111.csv")
```

# ====================Add participant ID column================== 
```{r}
# Add participant ID column 
a_107$Participant_ID <- 107
a_108$Participant_ID <- 108
a_109$Participant_ID <- 109
a_110$Participant_ID <- 110
a_111$Participant_ID <- 111
```

# ====================# Add activity column================== 
```{r}
# Add activity column 
a_107$activity 
a_108$activity 
a_109$activity 
a_110$activity 
a_111$activity 
```

# ====================# Append all participant ID CSVs================== 

```{r}
# Append all participant ID CSVs 
applewatch_all <- rbind (a_107, a_108, a_109, a_110, a_111)
```

# ====================# Add activity stage colum to csv ================== 
```{r}
# Add activity stage colum to csv 
applewatch_all$activity_stage <- ""
```

# ====================# Summary of statistical descriptives ================== 
```{r}
# Summary of statistical descriptives 
summary(applewatch_all)
```

# ====================# Summary of statistical descriptives using Stargazer ================== 

```{r}
# Summary of statistical descriptives using Stargazer 
stargazer(applewatch_all, type = "text")
```

```{r}
# Add summary by participant FIX ME 
# applewatch_all %>% 
  group_by(applewatch_all,Participant_ID, add = FALSE) %>%
    summarize(stargazer(applewatch_all, type = "text"))
```

```{r}
## Add stages for each participant
```

#================ #Scatterplot of Heart rate vs. Time, Condensed Scatter Plot ======================

```{r}  
#Scatterplot of Heart rate vs. Time, Condensed Scatter Plot 
ggplot(applewatch_all, aes(x = DateTime, y = Heart, colour=Participant_ID, group=Participant_ID)) + 
  geom_point() +
facet_wrap(~Participant_ID, scales ="free_y" )
```

```{r}
#Scatterplot of Calories vs. Time, Condensed Scatter Plot 
ggplot(applewatch_all, aes(x = DateTime, y = Calories, colour=Participant_ID, group=Participant_ID)) + 
  geom_point() +
facet_wrap(~Participant_ID, scales ="free_y")
```

```{r}
#Scatterplot of Steps vs. Time, Condensed Scatter Plot 
ggplot(applewatch_all, aes(x = DateTime, y = Steps, colour=Participant_ID, group=Participant_ID)) + 
  geom_point() +
facet_wrap(~Participant_ID, scales ="free_y")
```

```{r}
### INPUT Missing and create new variables

### Heart_impute  Calories_impute

### Redraw figures for each variable using missing data

https://www.analyticsvidhya.com/blog/2016/03/tutorial-powerful-packages-imputing-missing-values/
```


```{r}
#install MICE
install.packages("mice")
library(mice)
```

```{r}
#Tabular form of missing value present in each variable in a data set.
md.pattern(applewatch_all)
```
```{r}
#Visual representation of missing data
install.packages("VIM")
library(VIM)
applewatch_all_plot <- aggr(applewatch_all, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(applewatch_all), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
#Missing data: 8% of steps data, 11% of heart and calories data 
```
```{r}
#Impute the missing values with summary
#m - refers to 5 imputed data sets, maxit - refers to number of iterations taken to impute missing values, method-method used, predictive mean matching 
imputed_Data <- mice(applewatch_all, m=5, maxit = 50, method = 'pmm', seed = 500)
summary(imputed_Data)
```
```{r}
#Check imputed Heart values 
imputed_Data$imp$Heart
```
```{r}
#Check imputed Steps values 
imputed_Data$imp$Steps
```

```{r}
#Check imputed Calories values 
imputed_Data$imp$Calories
```

```{r}
#Get complete data ( 2nd out of 5)
completeData <- complete(imputed_Data,2)
```


```{r}
#build predictive model
fit <- with(data = applewatch_all, exp = lm(Heart ~ Calories + Steps)) 
```

setwd("Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/HealthData/Bo's working folder")
write.csv (applewatch_all, file='applewatch_all.csv')
```